Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-14 paper2_JNLS/Referee Reports/Ref1Response/Ref1.tex
NM

\begin{itemize}
\item First, thank you for these insightful comments. The referee is correct to point out that a sufficient amount of nonlinear interaction is  required for relaxation to the Gibbs measure, and we agree that this condition not being met is the most likely the explanation for formula (53) not matching the smallest-amplitude data in Fig. 8(c). We have inserted these points in the updated manuscript. In particular, see the passage in Section 3.5 (page 11):
\begin{quotation}
We also point out that a sufficient amount of nonlinear mixing is required for relaxation to the above Gibbs measure. In the linearized system, for example, modes propagate without interacting and hence the initial measure induced by the wave generator remains unchanged.
\end{quotation}
Also, see the passage describing Fig. 8(c) in Section 4.4 (page 22)
\begin{quotation}
The apparently less predictable behavior at small amplitudes can be attributed to the fact that, in order for the system to relax to the Gibbs measure, modes must interact through nonlinearity. For the smallest amplitude experiments, the amount of nonlinearity is apparently too small for  modes to mix sufficiently.
\end{quotation}
\item Have we included new references on integrable turbulence???
%\item The referee is correct that equilibrium statistical mechanics and the canonical ensemble is used here, not because it is rigorously justified, but as an effective theory that explains the data. It is true that the 1D KdV equation is an integrable system whose trajectories are constrained by an infinite number of conserved quantities. However, the {\em truncated} system does not possess these constraints (and pointed out in the original text).
%\begin{quotation}
%\end{quotation}
\end{itemize}

\noindent
\comment{
2. The authors may find it useful to compare their equation (53) to
 ``On the origin of heavy-tail statistics in equations of the Nonlinear Schrodinger type'', Onorato et al., Phys. Lett. A, 380, 89 (2016), 
 %where an analogous relationship is derived for NLS. It should be possible to relate the skewness to spectral variations, which may lead to further interesting investigations.
}

@@

>>>>

\begin{itemize}
\item First, thank you for these insightful comments. The referee is correct that a sufficient amount of nonlinear interaction is  required for relaxation to the Gibbs measure. We agree that it is most likely the failure of this condition being met that explains the discrepancy between formula (53) and the smallest-amplitude data in Fig. 8(c). We have inserted these points in the updated manuscript. First, see the passage in Section 3.5 (page 11):
\begin{quotation}
We also point out that a sufficient amount of nonlinear mixing is required for relaxation to the above Gibbs measure. In the linearized system, for example, modes propagate without interacting and hence the initial measure induced by the wave generator remains unchanged.
\end{quotation}
Second, see the passage describing Fig. 8(c) in Section 4.4 (page 22)
\begin{quotation}
The apparently less predictable behavior at small amplitudes can be attributed to the fact that, in order for the system to relax to the Gibbs measure, modes must interact through nonlinearity. For the smallest amplitude experiments, the amount of nonlinearity is apparently too small for  modes to mix sufficiently.
\end{quotation}
%
\item We thank the referee for drawing our attention to the vibrant field of integrable turbulence. We have now included a discussion to compare and contrast our statistical theory with that from integrable turbulence (as well as a few additional references). In particular, please see the new passage at the end of section 3.4
\begin{quotation}
We comment on some important differences between the KdV and TKdV dynamical systems. Besides momentum, energy, and Hamiltonian, KdV possesses in infinite sequence of additional invariants. Trajectories of KdV are therefore constrained by an infinite number of conserved quantities, associated with the fact that it is a completely integrable system whose long-time dynamics are dominated by coherent structures known as solitons. The analogues of these additional invari- ants, however, are not generally conserved in the truncated system; the only known invariants of TKdV are the three mentioned already: momentum, energy, and Hamiltonian. Dynamics of TKdV, rather than being dominated by coherent structures, become chaotic in long time and have been numerically observed to satisfy weak ergodicity (though a rigorous mathematical proof awaits) [2]. In this way, the theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence [54, 40, 10, 41], where integrability is exploited to uncover certain statistical features. We remind the reader that KdV is asymptotically valid only for large spatial scales and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV should be regarded as on equal footing as far as physical realism, provided that sufficiently many modes are considered. Where differences exist in long-time dynamics, it is unclear a priori which model, if either, more closely resembles reality, which underscores the importance of controlled laboratory experiments.
\end{quotation}
\end{itemize}
%\item The referee is correct that equilibrium statistical mechanics and the canonical ensemble is used here, not because it is rigorously justified, but as an effective theory that explains the data.

\noindent
\comment{
2. The authors may find it useful to compare their equation (53) to
 ``On the origin of heavy-tail statistics in equations of the Nonlinear Schrodinger type'', Onorato et al., Phys. Lett. A, 380, 89 (2016), where an analogous relationship is derived for NLS. It should be possible to relate the skewness to spectral variations, which may lead to further interesting investigations.
}

\begin{itemize}
\item Thank you for bringing this very relevant reference to our attention. We included this reference and, in addition, have found another reference, Onorato \& Suret 2016, which has analysis specific to KdV. We have now included a discussion of these works, including similarities and differences with our analysis. In particular, note that both of these references considered only uniform depth, whereas, since our work considers variable depth, there must be a formula linking the two ---  the statistical matching condition. See the passage at the end of Section 4.4:

\begin{quotation}
We remark that Eq. (53) bears similarity to a formula derived by Onorato \& Suret [36], in the context of constant-depth KdV, that relates variations in skewness to variations in spectral bandwidth. Indeed, since $\eta_t \approx c \eta_x$ to leading order, the term $\text{var}(\eta_x)$ in Eq. (53) could be interpreted as approximately the spectral bandwidth. We note that an analogous formula has been derived for the nonlinear Schrodinger equation relating kurtosis to bandwidth variations [34]. The present study differs in that it predicts a moment-bandwidth relation for waves propagating over variable depth, where it is the depth change that creates system disequilibrium. A small transition region connects two near-equilibrium systems, i.e. one far upstream and one far downstream. The link between these two equilibrium states is made mathematically precise by the statistical matching condition (34), which is the key ingredient needed to derive Eq. (53). This is in contrast to the simpler situation of waves propagating over constant depth, where spectral variations and the associated moment variations arise from out-of-equilibrium initial conditions [36, 34].
\end{quotation}

\end{itemize}

\noindent
\comment{
3. From the experimental point of view, have the authors considered corrections due to the second-order of the Stokes series? When the nonlinearity is important, the bound-modes impact on the skewness may be non-negligible. Is it possible to filter out such corrections in the experimental signal and then compare with the theory? May this explain why the ADC skewness jump is so much larger in the experiment than in the theory?
}

@@

%Upon satisfying consideration of the remarks above, I am ready to consider the manuscript suitable for publication in Journal of Nonlinear Science. The manuscript is well written, clear, instructive and original. The methods presented here, for the first time in such a complete and pedagogical way, tackle a problem of fluid mechanics with ideas from dynamical systems and statistical physics. The resulting method is general and of broad applicability in the realm of nonlinear physics.

### 2020-05-14 paper2_JNLS/paper.tex
NM

The momentum and energy defined in \eqref{MomEn} remain invariants of TKdV, with the same normalized values $\Mo[\uL] = 0$ and $\En[\uL] = 1$. Note that Parseval's identity implies
\begin{equation}
\En[\uL] = 2 \pi \sum_{k=1}^{\Lambda} \abs{\uhat_k}^2 = 1
\end{equation}
% The above agrees with the first line on top of p. 4 in Majda and Qi J Stat Phys 2019.
Thus, the dynamics of interest are confined to the unit hypersphere, $\En = 1$ in $\CC^{\Lambda}$.
In summary, the TKdV system possesses three important invariants: momentum, energy, and Hamiltonian. The untruncated KdV equation possesses an infinite sequence of additional invariants \cite{lax1975periodic, whitham2011linear}, but their truncated counterparts are not generally invariants of TKdV.

@@

	Differences in the detailed shapes of these downstream distributions are also visible. First, we point out that the experimental measurements involve numerical differentiation of  surface displacement extracted from optical images, a process that unavoidably amplifies any noise that is present. We must therefore proceed with caution in comparing the experiment and theory, recognizing the possibility that observed discrepancies may be due to these measurement errors. Nonetheless, we notice that the theoretically predicted distributions remain symmetric downstream and the experimental ones skew towards negative slope. As mentioned in Section \ref{experiments}, negative skewness is consistent with a right-moving wave of steep leading surface (i.e.~negative slope). Additionally, the peak of the experimental distribution appears sharper than that of the theory.

>>>>

The momentum and energy defined in \eqref{MomEn} remain invariants of TKdV, with the same normalized values $\Mo[\uL] = 0$ and $\En[\uL] = 1$. Note that Parseval's identity implies
\begin{equation}
\En[\uL] = 2 \pi \sum_{k=1}^{\Lambda} \abs{\uhat_k}^2 = 1
\end{equation}
Thus, the dynamics of interest are confined to the unit hypersphere, $\En = 1$ in $\CC^{\Lambda}$.
%In summary, the TKdV system possesses three important invariants: momentum, energy, and Hamiltonian.

\new{We comment on some important differences between the KdV and TKdV dynamical systems. Besides momentum, energy, and Hamiltonian, KdV possesses in infinite sequence of additional invariants. Trajectories of KdV are therefore constrained by an infinite number of conserved quantities, associated with the fact that it is a completely integrable system whose long-time dynamics are dominated by coherent structures known as solitons. The analogues of these additional invariants, however, are {\em not} generally conserved in the truncated system; the only known invariants of TKdV are the three mentioned already: momentum, energy, and Hamiltonian. Dynamics of TKdV, rather than being dominated by coherent structures, become chaotic in long time and have been numerically observed to satisfy weak ergodicity (though a rigorous mathematical proof awaits) \cite{bajars2013weakly}. In this way, the theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence \cite{zakharov2009turbulence, randoux2014intermittency, costa2014soliton, randoux2016nonlinear}, where  integrability is exploited to uncover certain statistical features. We remind the reader that KdV is asymptotically valid only for large spatial scales and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV should be regarded as on equal footing as far as physical realism, provided that sufficiently many modes are considered. Where differences exist in long-time dynamics, it is unclear {\em a priori} which model, if either, more closely resembles reality, which underscores the importance of controlled laboratory experiments.
}

@@

	Differences in the detailed shapes of these downstream distributions are also visible. First, we point out that the experimental measurements involve numerical differentiation of  surface displacement extracted from optical images, a process that unavoidably amplifies any noise that is present. We must therefore proceed with caution in comparing the experiment and theory, recognizing the possibility that observed discrepancies may be due to these measurement errors. Nonetheless, we notice that the theoretically predicted distributions remain symmetric downstream and the experimental ones skew towards negative slope. As mentioned in Section \ref{experiments}, negative skewness is consistent with a right-moving wave of steep leading surface (i.e.~negative slope). Additionally, the peak of the experimental distribution appears sharper than in the theory.
